---
title: "Course Functions"
author: "Antoine Redier"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Description 

This package provides with enhenced versions of the five major functions studied in the R introduction course of the Data Science for business graduate degree of Ecole Polytechnique

#### csv_reader

function that reads all the csv files in a directory and outputs them in a list of data.frame: 

```{r}
library(coursefunctions)

csv_reader("../data-raw")
```
#### xlsx_reader

reads alls the sheets of an ecxel document and retruns them in a list of data.frame

```{r}
library(coursefunctions)

xlsx_reader("../data-raw/test.xlsx")
```

#### draw_name

draws the number of babies born with a specific name and sex in a France between 1900 and 2015 

```{r}
library(coursefunctions)

draw_name("Antoine", "M")
```

#### draw_multiple_name 

same thing with multiple names 

```{r}
library(coursefunctions)

draw_multiple_name(c("Antoine", "Marie"))
```

####Save as CSV 

saves a csv after verifying the parameters 

```{r}
library(coursefunctions)

df <- read.csv2("../data-raw/titanic_test.csv")

save_as_csv(df, "../data-raw/titanic_test2.csv")
```

